Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-06-28 PaperOnSmoothing/draft-31052016.tex
MAC randomization in methods section + comments for Philip in methods section
corrections in MAC subsection of methods section

Formally,  (now write formulas)

@@

Thus, when estimating crowd density, we ignore the MAC devices that have a randomized address and at the end we multiply the crowd density by 1.0225, to account for the ignored MAC devices. We choose factor 1.0225 to allow for a safety margin: in the peaks of the graph in Fig. \ref{fig:randomized} the values are 0.025, and we would rather overestimate than underestimate the crowd density. 
Note that this ratio should be re-computed periodically, to account for the changing conditions at the smart phones market.

>>>>

Formally,  (to Philip: now write formulas, please )

@@

Thus, when estimating crowd density, we ignore the MAC devices that have a randomized address and at the end we multiply the crowd density by 1.0225, to account for the ignored MAC devices. We choose factor 1.225 to allow for a safety margin: in the peaks of the graph in Fig. \ref{fig:randomized} the values are 0.225, and we would rather overestimate than underestimate the crowd density. 
Note that this ratio should be re-computed periodically, to account for the changing conditions at the smart phones market.
